The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-07-05 analysis/paper/paper.qmd
Update topic model script

# Load packages ----
## List packages to be loaded
packages <- c(
  "here",                               # Managing paths
  "tidyverse", "reshape2", "widyr",     # Data manipulation and visualisation
  "furrr",                              # Parallel use of purrr::map() functions
  "tidytext", "SnowballC", "tm",        # Text processing and analysis
  "topicmodels", "LDAvis",              # Topic modeling
  "tidygeocoder",                       # Working with spatial data
  "igraph", "ggraph"                    # Network analysis and visualization
)

@@

Similar to clustering on numeric data, topic modeling is a method of unsupervised classification of topics found in a group of documents [@silge2017]. We used the Latent Dirichlet Allocation (LDA) algorithm for topic modeling. In LDA, each document is a mixture of topics and each topic is a mixture of words. The probability of a term being part of a topic is given by the $\beta$ (beta) statistic, while the probability of a document being part of a topic is given by the $\gamma$ (gamma) statistic.

The number of topics was empirically determined with the `ldatuning` package [@???].

@@

# Add topic pseudo-names based on the top 5 words in each topic
topic_names <- name_topics(beta)

@@

# What is the dominant topic in each document?
N = 20
topic_prop_examples <- theta[1:N,]
colnames(topic_prop_examples) <- topic_names
vizDataFrame <- melt(cbind(data.frame(topic_prop_examples), 
                           document = factor(rownames(topic_prop_examples))), 
                     variable.name = "topic", id.vars = "document")  
ggplot(data = vizDataFrame, aes(topic, value, fill = document), ylab = "proportion") + 
  geom_bar(stat="identity") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +  
  coord_flip() +
  facet_wrap(~ document, ncol = 5) +
  theme(legend.position = "none")
```

@@

topicmodels_json_ldavis <- function(fitted, corpus, doc_term) {

  phi <- topicmodels::posterior(fitted)$terms |> as.matrix
  theta <- topicmodels::posterior(fitted)$topics |> as.matrix
  vocab <- colnames(phi)
  doc_length <- vector()

  for (i in 1:length(corpus)) {
    temp <- paste(corpus[[i]]$content, collapse = " ")
    doc_length <- c(doc_length, stringi::stri_count(temp, regex = '\\S+'))
  }

  temp_frequency <- doc_term |> as.matrix
  freq_matrix <- data.frame(ST = colnames(temp_frequency),
                            Freq = colSums(temp_frequency))
  rm(temp_frequency)

  json <- LDAvis::createJSON(phi = phi,
                             theta = theta,
                             doc.length = doc.length,
                             vocab = vocab,
                             term.frequency = freq_matrix$Freq)
}

LDAvis::serVis(emu_lda_json, out.dir = "vis", open.browser = FALSE)

@@

# Extract topics as mixtures of terms from LDA model
emu_topics <- tidy(emu_lda, matrix = "beta")

# The top n most common words in each topic
emu_theses_top_terms <- get_top_words_per_topic(emu_topics, 20)

>>>>

# Load packages ----
## List packages to be loaded
packages <- c(
  "here",                               # Managing paths
  "tidyverse", "reshape2", "widyr",     # Data manipulation and visualisation
  "furrr",                              # Parallel use of purrr::map() functions
  "tidytext", "SnowballC", "tm",        # Text processing and analysis
  "topicmodels", "LDAvis", "tsne",      # Topic modeling
  "tidygeocoder",                       # Working with spatial data
  "igraph", "ggraph"                    # Network analysis and visualization
)

@@

Similar to clustering on numeric data, topic modeling is a method of unsupervised classification of topics found in a group of documents [@silge2017]. We used the Latent Dirichlet Allocation (LDA) algorithm for topic modeling. In LDA, each document is a mixture of topics and each topic is a mixture of words. The probability of a term being part of a topic is given by the $\beta$ (beta) statistic, while the probability of a document being part of a topic is given by the $\theta$ (theta) statistic.

The number of topics was qualitatively determined

@@

# Add pseudo-names to topics based on the top 5 words in each topic
topic_names <- name_topics(beta)

@@

# What is the dominant topic in each document?
N = 20
topic_prop_examples <- theta[1:N,]
colnames(topic_prop_examples) <- topic_names
vizDataFrame <- melt(cbind(data.frame(topic_prop_examples), 
                           document = factor(rownames(topic_prop_examples))), 
                     variable.name = "topic", id.vars = "document")  
ggplot(data = vizDataFrame, aes(topic, value, fill = document), ylab = "proportion") + 
  geom_bar(stat="identity") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +  
  coord_flip() +
  facet_wrap(~ document, ncol = 5) +
  theme(legend.position = "none")

@@

# TODO check if this can be included in the Shiny dashboard
# Function to approximate the distance between topics
svd_tsne <- function(x) tsne(svd(x)$u)

# Convert DTM into JSON required by the LDAvis package
json <- LDAvis::createJSON(
  phi = beta, 
  theta = theta, 
  doc.length = rowSums(as.matrix(emu_dtm)), 
  vocab = colnames(emu_dtm), 
  term.frequency = colSums(as.matrix(emu_dtm)),
  mds.method = svd_tsne,
  plot.opts = list(xlab="", ylab="")
)

# Visualise topics model with LDAvis
LDAvis::serVis(json)

@@

# Extract topics as mixtures of terms from LDA model
beta_tidy <- tidy(emu_lda, matrix = "beta")

# The top n most common words in each topic
emu_theses_top_terms <- get_top_words_per_topic(beta_tidy, 20)
